\vskip-0.6in Trade Agreements in the Shadow of Lobbying\protect\footnote{Formerly circulated under the title ``Trade Agreements, Lobbying and Separation of Powers''}

### 2016-02-01 game-tree.tex
fix game-tree for opportunity to break

\addtolength{\textwidth}{1.3in}
\addtolength{\oddsidemargin}{-.65in} %left margin
\addtolength{\evensidemargin}{-.65in}
\setlength{\textheight}{9in}
\setlength{\topmargin}{-.5in}
\setlength{\headheight}{0.0in}
\setlength{\footskip}{.375in}
\renewcommand{\baselinestretch}{1.0}
%\linespread{1.5}
\usepackage{setspace}
\doublespacing

@@

% disables chapter, section and subsection numbering
%\setcounter{secnumdepth}{-1}

@@

\newtheorem{definition}{Definition}
\newtheorem{theorem}{Theorem}
\newtheorem{lemma}{Lemma}
\newtheorem*{lemma*}{Lemma}
\newtheorem{corollary}{Corollary}
\newtheorem{assumption}{Assumption}
\newtheorem{fact}{Fact}
\newtheorem{result}{Result}

\newcommand{\ve}{\theta}
\newcommand{\ta}{\theta}
\newcommand{\ov}{\overline}
\newcommand{\un}{\underline}
\newcommand{\al}{\alpha}
\newcommand{\Ta}{\Theta}
\newcommand{\expect}{\mathbb{E}}
\newcommand{\Bt}{B(\bm{\tau^a})}
\newcommand{\bta}{\bm{\tau^a}}
\newcommand{\bte}{\bm{\tau^E}}
\newcommand{\btn}{\bm{\tau^n}}
\newcommand{\ga}{\gamma}

@@

\tikzset{
% Two node styles for game trees: solid and hollow
solid node/.style={circle,draw,inner sep=1.5,fill=black},
hollow node/.style={circle,draw,inner sep=1.5,fill=white}
%non node/.style={circle,draw,inner sep=.1,fill=black}
}
\begin{tikzpicture}[scale=1.5,font=\footnotesize, grow=right]
% Specify spacing for each level of the tree
\tikzstyle{level 1}=[level distance=10mm,sibling distance=10mm]
\tikzstyle{level 2}=[level distance=10mm,sibling distance=10mm]
% The Tree
\node(0)[solid node,label=above:{$E,E^*$}]{} 
child{node(1)[solid node,label=below:{$0$}]{}}
child{[white] node(2)[solid node,xshift=12,label=above:{L}]{}  
	child{[black] node(4)[solid node,label=below:{$0$}]{}}
	child{[white] node(5)[hollow node,xshift=12]{} 
		child{[black] node(7)[solid node,label=below:{$-\infty$}]{}}
		child{[white] node(8)[solid node,xshift=12]{}  
			child{[black] node(10)[solid node]{}  }
			child{[black] node(12)[solid node]{}  
				child[sibling distance=5mm]{[black] node(13)[solid node,label=below:{$0$}]{}}
				child{[white] node(15)[solid node,xshift=7]{} 
					child[sibling distance=5mm]{[black] node(16)[solid node,label=below:{$0$}]{} }
					child{[white] node(18)[hollow node,xshift=12,label=left:{}]{}  }
					child[sibling distance=5mm]{[black] node(17)[solid node,label=above:{$\infty$}]{} }
					edge from parent node[black, xshift=20]{$e_n$} 
					}
				child[sibling distance=5mm]{[black] node(14)[solid node,label=above:{$\infty$}]{} }
				}
			edge from parent node[black, xshift=23]{$\ta$} 
			}
		child{[black] node(9)[solid node,label=above:{$\infty$}]{} }
		edge from parent node[black, xshift=23]{$e_b$} 
		}
	child{[black] node(6)[solid node,label=above:{$\infty$}]{}}
	edge from parent node[black, xshift=23]{$\bta$} 
	}
child{node(3)[solid node,label=above:{$\infty$}]{}
}
;
% information set
    \draw[solid,bend right](1)to(3);
		\draw[solid,bend right](4)to(6);
		\draw[solid,bend right](7)to(9);
		\draw[solid,bend right](13)to(14);
		\draw[solid,bend right](16)to(17);
% labels
		\node[above,xshift=5,yshift=5]at(2){$L$}; 
		\node[above,xshift=5,yshift=5]at(5){$N$}; 
		\node[above,xshift=8,yshift=5]at(8){$Leg$}; 
		\node[above,xshift=5,yshift=5]at(12){$L$}; 
		\node[above,xshift=7,yshift=5]at(15){$Leg$}; 
		\node[left, xshift=-2]at(18){$\tau^n$}; 
		\node[below left,yshift=-10]at(12){Break}; 
		\node[below left,yshift=1]at(10){Abide}; 
		\draw[solid](5)circle(.05cm);
		\draw[solid](0)circle(.15cm);
		\node[right]at (10) {$W_E\left(\bta\right),$};
		\node[right,yshift=-10]at (10) {$\pi\left(\tau^a\right)-e_b,$};
		\node[right,yshift=-20]at (10) {$W_{ML}\left(\ga(e_b,\ta_b),\bta\right)$};
		\node[right]at (18) {$W_E\left(\btn\right),$};
		\node[right,yshift=-10]at (18) {$\pi\left(\tau^n\right)-e_b -e_n,$};
		\node[right,yshift=-20]at (18) {$W_{ML}\left(\ga(e_n,\ta_n),\btn\right)$};

\end{tikzpicture}

@@

%child{[black] node(4)[solid node,label=below:{$0$}]{} edge from parent node[left]{$C$}}
%child{[black] node(6)[solid node,label=above:{$\infty$}]{} edge from parent node[right]{$D$}}

>>>>

\addtolength{\textwidth}{1.3in}
\addtolength{\oddsidemargin}{-.65in} %left margin
\addtolength{\evensidemargin}{-.65in}
\setlength{\textheight}{9in}
\setlength{\topmargin}{-.5in}
\setlength{\headheight}{0.0in}
\setlength{\footskip}{.375in}
\renewcommand{\baselinestretch}{1.0}
\usepackage{setspace}
\doublespacing

@@

% disables chapter, section and subsection numbering
\setcounter{secnumdepth}{-1}

@@

\newcommand{\ta}{\theta}
\newcommand{\al}{\alpha}
\newcommand{\Ta}{\Theta}
\newcommand{\expect}{\mathbb{E}}
\newcommand{\Bt}{B(\bm{\tau^a})}
\newcommand{\bta}{\bm{\tau^a}}
\newcommand{\bte}{\bm{\tau^E}}
\newcommand{\btn}{\bm{\tau^n}}
\newcommand{\ga}{\gamma}

@@

\tikzset{
% Two node styles for game trees: solid and hollow
solid node/.style={circle,draw,inner sep=1.5,fill=black},
hollow node/.style={circle,draw,inner sep=1.5,fill=white}
%non node/.style={circle,draw,inner sep=.1,fill=black}
}
\begin{tikzpicture}[scale=1.5,font=\footnotesize, grow=right]
% Specify spacing for each level of the tree
\tikzstyle{level 1}=[level distance=10mm,sibling distance=8mm]
\tikzstyle{level 2}=[level distance=8mm,sibling distance=8mm]
% The Tree
\node(0)[solid node,label=above:{$E,E^*$}]{} 
child{node(1)[solid node,label=below:{$0$}]{}}
child{[white] node(2)[solid node,xshift=12,label=above:{L}]{}  
	child{[black] node(4)[solid node,label=below:{$0$}]{}}
	child{[white] node(5)[hollow node,xshift=12]{} 
	 child[sibling distance=11mm]{[black] node(22)[solid node]{}  }
	 child[sibling distance=11mm]{[black] node(23)[hollow node]{}  
		child[sibling distance=8mm]{[black] node(7)[solid node,label=below:{$-\infty$}]{}}
		child[sibling distance=8mm]{[white] node(8)[solid node,xshift=12]{}  
			child[sibling distance=10mm]{[black] node(10)[solid node]{}  }
			child[sibling distance=10mm]{[black] node(12)[solid node]{}  
				child[sibling distance=5mm]{[black] node(13)[solid node,label=below:{$0$}]{}}
				child{[white] node(15)[solid node,xshift=7]{} 
					child[sibling distance=5mm]{[black] node(19)[solid node,label=below:{$-\infty$}]{}}
					child{[white] node(21)[solid node,xshift=7]{} 
						child[sibling distance=5mm]{[black] node(16)[solid node,label=below:{$0$}]{} }
						child{[white] node(18)[hollow node,xshift=12,label=left:{}]{}  }
						child[sibling distance=5mm]{[black] node(17)[solid node,label=above:{$\infty$}]{} }
						edge from parent node[black, xshift=16]{$\ta_n$} 
						}
					child[sibling distance=5mm]{[black] node(21)[solid node,label=above:{$\infty$}]{} }
					edge from parent node[black, xshift=15]{$e_n$} 
				}
				child[sibling distance=5mm]{[black] node(14)[solid node,label=above:{$\infty$}]{} }
				}
			edge from parent node[black, xshift=20]{$\ta_b$} 
			}
		child[sibling distance=8mm]{[black] node(9)[solid node,label=above:{$\infty$}]{} }
		}
	 edge from parent node[black, xshift=20]{$e_b$} 	
	 }
	child{[black] node(6)[solid node,label=above:{$\infty$}]{}}
	edge from parent node[black, xshift=23]{$\bta$} 
	}
child{node(3)[solid node,label=above:{$\infty$}]{}
}
;
% information set
    \draw[solid,bend right](1)to(3);
		\draw[solid,bend right](4)to(6);
		\draw[solid,bend right](7)to(9);
		\draw[solid,bend right](13)to(14);
		\draw[solid,bend right](16)to(17);
		\draw[solid,bend right](19)to(21);
% labels
		\node[above,xshift=3,yshift=5]at(2){$L$}; 
		\node[above,xshift=1,yshift=5]at(23){$N$}; 
		\node[above,xshift=3,yshift=5]at(5){$N$}; 
		\node[above,xshift=6,yshift=5]at(8){$Leg$}; 
		\node[above,xshift=5,yshift=5]at(12){$L$};
		\node[above,xshift=13,yshift=-17]at(21){$Leg$}; 
		\node[above,xshift=7,yshift=5]at(15){$N$}; 
		\node[left, xshift=-2]at(18){$\tau^n$}; 
		\node[below left,yshift=-12]at(12){Break}; 
		\node[below left,yshift=4]at(10){Abide}; 
		\draw[solid](5)circle(.05cm);
		\draw[solid](0)circle(.15cm);
		\node[right]at (10) {$W_E\left(\bta\right),$};
		\node[right,yshift=-10]at (10) {$\pi\left(\tau^a\right)-e_b,$};
		\node[right,yshift=-20]at (10) {$W_{ML}\left(\ga(e_b,\ta_b),\bta\right)$};
		\node[right]at (18) {$W_E\left(\btn\right),$};
		\node[right,yshift=-10]at (18) {$\pi\left(\tau^n\right)-e_b -e_n,$};
		\node[right,yshift=-20]at (18) {$W_{ML}\left(\ga(e_n,\ta_n),\btn\right)$};
		\node[right,yshift=-5]at (22) {$W_E\left(\bta\right),$};
		\node[right,yshift=-15]at (22) {$\pi\left(\tau^a\right)-e_b,$};
		\node[right,yshift=-25]at (22) {$W_{ML}\left(\ga(e_b,\ta_b),\bta\right)$};
		\node[below left,xshift=-4,yshift=8]at(23){Opp.}; 
		\node[below left,xshift=-4,yshift=-10]at(23){(o)}; 
		\node[below left,xshift=-3,yshift=7]at(22){No opp.}; 
		\node[below left,xshift=6,yshift=20]at(22){(1-o)}; 
\end{tikzpicture}

@@
